Quality of Service with Software Defined Network.

### 2017-03-04 report/paper.tex
create image folder

\section{Needs and Gools}\label{sec:obb} %obbiettivi ed esigenze controllare 
The main gool of this experience is to obtain statistics on realtime traffic in order to reroute traffic based on QoS or other reasons. 
%correggere
  \subsection{Adaptability of the network}
  Made Network Adaptable means poter dirottare il traffico in real time to ensura a lot of demands. For example we have to avoid link congestion, 
  but we can prefer reroute some hosting traffic to peggiorare it's performance because of it's evil traffic.
  To reach this gools we need to have a global knowledge on the network and we have to modify the routing table on every routerboard with a 
  global scope.
  The performance of a single connection and entire network can ensure various type of metrics.
  In order to assicurare queste ci serve una struttura dati che si aggiorna costantemente nella quale immagazzinare le statistiche dei link 
  in modo all'occorrenza di trovare il percordo migliore per ogni singolo flusso dati.
  \#TODO MATTEO
  \subsection{Exterior comunication}
  \#TODO pitt

\section{Instrument}\label{sec:instrument}
\#TODO matteo
  \subsection{Controller}
  The controller that we use is POX, it's repository is at this link \url{https://github.com/noxrepo/pox}. 
  POX is an opensource python controller, it is an evolution of NOX a controller developed on C language.
  The documentation about the progect is present at this link \url{https://openflow.stanford.edu/display/ONL/POX+Wiki}.
  The only problem to use this controller is that it support only the first version of OpenFlow1.0.

  The controller run inside a VirtualMachine on our personal computer, offered by SDN hub \cite{VM}. This VM use UBUNTU like OS and version 2.7.6 of
  Python that is sufficient for POX that's required version 2.7.
  % \#TODO matteo da correggere e completare
  \subsection{Router Board}
  The router board that we used is MikroTik miniROUTER RouterBOARD 450G. This Router Board virtualize an OpenFlow switch that support 
  OpenFlow v1.0. The main caraptheristics is that it has only 5 ethernet port this is a limitation because consider that one of this port it is 
  used to connect conntroller and with other port we have made host and other routerboard connection.

  %\#TODO matteo ( parlare del firmware utilizzato nella routerboard) correggere e completare

@@

\begin{thebibliography}{99}
	\bibitem{pox} POX \url{https://openflow.stanford.edu/display/ONL/POX+Wiki}
	\bibitem{openflow} OpenFlow \url{http://flowgrammable.org/sdn/openflow/}
	\bibitem{pox_repo} POX's repository \url{https://github.com/noxrepo/pox}
	\bibitem{VM} Virtual Machine \url{http://sdnhub.org/tutorials/pox/}
	\bibitem{router_board} Router Board \url{https://www.senetic.it/product/RB450G}
	\bibitem{netoworkx} NetworkX python's library \url{https://networkx.github.io/}
	\bibitem{ONF} Open Networking Foundation \url{https://www.opennetworking.org/sdn-resources/technical-library}
	\bibitem{ONF_report} v1.5.1 OpenFlow report \url{https://www.opennetworking.org/sdn-resources/technical-library}

\end{thebibliography}

>>>>

\section{Needs and Gools}\label{sec:obb} %obbiettivi ed esigenze controllare 
The main gool of this experience is to develop a small SDN network in a lab with real hardware
in orther to understood come a livello pratico si possa implementare  a QoS service in a SDN scenarois.
Our network have to manage traffic with a global scope, in order to evolve in base on different parameters.
Inoltre the SDN network need to interact with world wide web efficently.
%correggere
  \subsection{Adaptability of the network}
  Made Network Adaptable means poter dirottare il traffico in real time to ensure a lot of demands. For example we have to avoid link congestion, 
  but we can prefer reroute some hosting traffic to peggiorare it's performance because of it's evil traffic.
  To reach this gools we need to have a global knowledge on the network and we have to modify the routing table on every routerboard with a 
  global scope.
  The performance of a single connection and entire network can ensure various type of metrics.
  In order to assicurare queste ci serve una struttura dati che si aggiorna costantemente nella quale immagazzinare le statistiche dei link 
  in modo all'occorrenza di trovare il percordo migliore per ogni singolo flusso dati.
  \#TODO MATTEO
  \subsection{Exterior comunication}
  \#TODO pitt

\section{Instrument}\label{sec:instrument}
\#TODO matteo
  \subsection{Controller}
  The controller that we use is POX, the software is opensource and it is write with Python, it is based on SDN and support OpenFlow.
  The software use the version 2.7 of Python.
  It's repository is at this link \url{https://github.com/noxrepo/pox} and a lot of documentation about the progect 
  is present at this link \url{https://openflow.stanford.edu/display/ONL/POX+Wiki}.
  The only problem to use this controller is that it support only the first version of OpenFlow1.0.
  \\
  The controller run inside a VirtualMachine on our personal computer, 
  the VM is offered by SDN hub on this site: \url{http://sdnhub.org/tutorials/sdn-tutorial-vm/}. 
  This VM is a 64-bit Ubuntu 14.04 that has a number of SDN software and tools installed.
  % \#TODO matteo da correggere e completare
  \subsection{Router Board}
  The router board that we used is MikroTik miniROUTER RouterBOARD 450G. This Router Board virtualize an OpenFlow switch that support 
  OpenFlow v1.0\cite{routerboard_doc}. 
  \begin{itemize}
   \item CPU		AR7161 680MHz
   \item Memory		256MB DDR SDRAM onboard memory
   \item Data storage	512MB onboard NAND memory chip, microSD card slot (on reverse)
   \item Ethernet 	Three 10/100/1000 Mbit/s Gigabit Ethernet ports supporting Auto-MDI/X
   \item Serial port 	One DB9 RS232C asynchronous serial port
  \end{itemize}
  \textbf{firmware} the current version is: '' da gercare col comando: system routerboard print ''
  \newline
  The \textbf{Operating System} that they use is MikroTik RouterOS ( cercare la versione installata) \cite{routeboard_software}.
  \newline
  One limitation of this routerboard is that it has only 5 ethernet port this is a limitation because consider that one of this port it is 
  used to connect conntroller and with other port we have made host and other routerboard connection.

  %correggere e completare Matteo

@@

\begin{thebibliography}{99}
	\bibitem{pox} POX \url{https://openflow.stanford.edu/display/ONL/POX+Wiki}
	\bibitem{openflow} OpenFlow \url{http://flowgrammable.org/sdn/openflow/}
	\bibitem{pox_repo} POX's repository \url{https://github.com/noxrepo/pox}
	\bibitem{VM} Virtual Machine \url{http://sdnhub.org/tutorials/pox/}
	\bibitem{router_board} Router Board \url{https://www.senetic.it/product/RB450G}
	\bibitem{netoworkx} NetworkX python's library \url{https://networkx.github.io/}
	\bibitem{ONF} Open Networking Foundation \url{https://www.opennetworking.org/sdn-resources/technical-library}
	\bibitem{ONF_report} v1.5.1 OpenFlow report \url{https://www.opennetworking.org/sdn-resources/technical-library}
	\bibitem{routerboard_doc} RouterBOARD 450G MikroTik documentation \url{http://www.routerboard.sk/files/pdf/rb450g_manual.pdf}
	\bibitem{routeboard_software} RouterBOARD MikroTik Software \url{https://mikrotik.com/software}
\end{thebibliography}
